### 2020-08-10 benchmarking/benchmarkingVM/ESS_round2.tex
results update

% Created by tikzDevice version 0.12.3 on 2020-08-07 14:28:37
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries Comparison of adapt (\textit{real}) and \textit{cat}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/chain [\textit{cat}]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/chain [adapt (\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{gray}{0.91}

\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (  0.00,370.60) --
	(207.56,578.16) --
	(284.41,578.16) --
	(284.41,491.97) --
	(  0.00,207.56) --
	cycle;
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (  0.00,343.43) --
	(234.73,578.16) --
	(284.41,578.16) --
	(284.41,519.15) --
	(  0.00,234.73) --
	cycle;
\definecolor{fillColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00,316.25) --
	(261.91,578.16) --
	(284.41,578.16) --
	(284.41,546.32) --
	(  0.00,261.91) --
	cycle;

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (138.85,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,431.83) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (111.68,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,404.66) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 82.85,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,377.49) {$4\times$};

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.85,501.35) --
	(160.70,501.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.77,498.73) --
	(156.77,503.66);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.77,498.12) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.10,505.21) --
	(226.15,505.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.23,503.12) --
	(224.23,507.10);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.23,501.18) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.91,510.62) --
	(195.69,510.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.30,510.51) --
	(195.30,510.72);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.30,506.58) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.45,465.30) --
	(158.07,465.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (154.63,461.56) --
	(154.63,468.44);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.63,461.27) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,486.93) --
	(159.52,486.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.06,482.33) --
	(153.06,490.65);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.06,484.03) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.81,519.93) --
	(232.76,519.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.29,519.53) --
	(232.29,520.32);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (232.29,517.02) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.38,481.29) --
	(197.55,481.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.14,479.06) --
	(195.14,483.29);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.14,478.06) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.44,517.15) --
	(231.91,517.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.19,515.64) --
	(231.19,518.55);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (231.19,513.12) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.86,520.80) --
	(226.63,520.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.25,520.64) --
	(226.25,520.95);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.25,516.76) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.50,451.92) --
	(178.74,451.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.28,448.49) --
	(174.28,454.83);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.28,447.88) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.34,477.13) --
	(194.89,477.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.89,473.94) --
	(191.89,479.87);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.89,474.22) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.29,524.26) --
	(235.63,524.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.46,523.85) --
	(235.46,524.66);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (235.46,521.35) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (219.41,503.79) --
	(222.44,503.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.99,500.06) --
	(220.99,506.92);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.99,500.56) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.74,495.12) --
	(212.21,495.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.55,492.24) --
	(210.55,497.62);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.55,491.08) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.33,521.42) --
	(228.35,521.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.85,521.06) --
	(227.85,521.77);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.85,517.38) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.31,503.68) --
	(212.31,503.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.41,503.51) --
	(210.41,503.85);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.41,499.64) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.56,505.84) --
	(217.05,505.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.93,502.42) --
	(214.93,508.74);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (214.93,502.93) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.33,496.74) --
	(152.55,496.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.01,490.27) --
	(141.01,501.59);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.01,493.51) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.17,497.06) --
	(223.98,497.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.95,494.75) --
	(218.95,499.12);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.95,493.03) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.87,510.44) --
	(136.69,510.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.77,509.25) --
	(132.77,511.57);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (132.77,506.41) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (122.43,470.48) --
	(153.27,470.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.38,460.23) --
	(143.38,477.18);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.38,466.45) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.53,499.18) --
	(134.19,499.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (128.53,493.87) --
	(128.53,503.35);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (128.53,496.28) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.21,524.80) --
	(235.92,524.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.57,524.57) --
	(235.57,525.02);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (235.57,521.89) {$\mu$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.15,508.68) --
	(210.57,508.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.05,505.52) --
	(206.05,511.41);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.05,505.46) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.79,509.64) --
	(219.64,509.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.40,499.41) --
	(207.40,516.32);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.40,505.60) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.29,518.51) --
	(227.21,518.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.27,517.93) --
	(226.27,519.08);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.27,514.48) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.98,478.53) --
	(195.19,478.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.02,472.24) --
	(190.02,483.29);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.02,474.50) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.02,507.50) --
	(212.05,507.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.06,502.00) --
	(211.06,511.78);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.06,504.59) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.89,524.89) --
	(238.66,524.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.87,523.29) --
	(236.87,526.36);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (236.87,521.98) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.69,491.89) --
	(181.70,491.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.93,489.89) --
	(178.93,493.70);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.93,488.66) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.17,513.22) --
	(230.44,513.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.82,511.43) --
	(229.82,514.87);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (229.82,509.19) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.44,515.26) --
	(219.18,515.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.81,514.88) --
	(218.81,515.64);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.81,511.23) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.99,482.35) --
	(176.42,482.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.05,479.47) --
	(173.05,484.86);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.05,478.32) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.60,487.67) --
	(185.47,487.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.18,486.01) --
	(183.18,489.20);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.18,484.76) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.29,519.28) --
	(230.98,519.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.64,518.95) --
	(230.64,519.61);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (230.64,516.38) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.39,505.99) --
	(174.41,505.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.66,505.16) --
	(169.66,506.79);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.66,502.77) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.75,506.32) --
	(230.90,506.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.39,504.70) --
	(229.39,507.81);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (229.39,502.28) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.03,511.42) --
	(206.39,511.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.21,511.15) --
	(206.21,511.69);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.21,507.39) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.24,482.46) --
	(177.13,482.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.28,481.27) --
	(175.28,483.58);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.28,478.43) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.62,482.96) --
	(187.77,482.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.37,480.13) --
	(185.37,485.43);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.37,480.05) {$\sigma$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- (230.34,338.88);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 94.93,338.88) -- ( 94.93,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.07,338.88) -- (140.07,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.20,338.88) -- (185.20,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.34,338.88) -- (230.34,333.90);

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 94.93,320.95) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (140.07,320.95) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (185.20,320.95) {1000};

>>>>

% Created by tikzDevice version 0.12.3 on 2020-08-10 16:04:21
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries adapt (\textit{real}) vs. adapt (\textit{cat})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [adapt (\textit{cat})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [adapt (\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,374.64) --
	(203.52,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,490.17) --
	(  0.00,203.52);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00,346.12) --
	(232.04,578.16);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,518.69) --
	(  0.00,232.04);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00,317.60) --
	(260.56,578.16);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,547.21) --
	(  0.00,260.56);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,435.87) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,407.35) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,378.83) {$4\times$};

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.83,462.17) --
	(104.39,462.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.95,455.39) --
	(100.95,467.26);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (100.95,458.94) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.25,462.51) --
	(190.79,462.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.21,460.09) --
	(180.21,464.68);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.21,458.48) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.00,476.56) --
	(103.04,476.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.41,475.30) --
	( 99.41,477.74);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.41,472.52) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.19,434.62) --
	(105.17,434.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (102.83,423.86) --
	(102.83,441.65);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (102.83,430.59) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.73,464.74) --
	( 95.52,464.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.46,459.17) --
	( 90.46,469.12);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 90.46,461.83) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.57,483.53) --
	(194.99,483.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.78,482.91) --
	(194.78,484.13);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.78,480.62) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.61,467.01) --
	(116.13,467.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.49,464.26) --
	(109.49,469.44);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (109.49,463.79) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.07,471.07) --
	(193.44,471.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.83,468.87) --
	(191.83,473.05);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.83,467.03) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.54,476.74) --
	(164.84,476.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.69,476.63) --
	(164.69,476.85);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.69,472.71) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.97,429.18) --
	(112.07,429.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (107.26,425.26) --
	(107.26,432.48);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (107.26,425.15) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.25,451.88) --
	(115.87,451.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.51,447.05) --
	(110.51,455.79);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (110.51,448.98) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.12,485.74) --
	(196.43,485.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.27,485.16) --
	(196.27,486.31);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.27,482.84) {$\kappa$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.15,474.71) --
	(181.63,474.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.43,471.39) --
	(177.43,477.57);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.43,471.49) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.21,475.71) --
	(184.09,475.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.98,464.98) --
	(174.98,482.73);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.98,471.68) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.98,485.03) --
	(197.78,485.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.38,484.42) --
	(197.38,485.62);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.38,481.00) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.24,443.07) --
	(164.70,443.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.71,436.47) --
	(158.71,448.06);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.71,439.03) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.58,473.47) --
	(182.90,473.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.86,467.70) --
	(180.86,477.96);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.86,470.56) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.48,498.31) --
	(212.33,498.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.49,497.03) --
	(210.49,499.52);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.49,495.41) {$\kappa$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,338.88);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 97.17,338.88) -- ( 97.17,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54,338.88) -- (144.54,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.91,338.88) -- (191.91,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.28,338.88) -- (239.28,333.90);

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 97.17,320.95) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (144.54,320.95) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (191.91,320.95) {1000};
